Comparative study of Dask and Spark for neuroimaging pipelines\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Natural Sciences and Engineering Research Council}

### 2019-06-13 latex/paper.tex
Modified the spark and dask bag engine sub-section

\textbf{PySpark.RDD \cite{spark-rdd}}

\textbf{Dask.bag \cite{dask-bag}}

\textbf{Dask.delayed \cite{dask-delayed}}

\textbf{Dask.futures \cite{dask-futures}}

@@

%% Incrementation
\subsubsection{\textbf{Incrementation}}
As our first experiment to benchmark the frameworks we used a simple incrementation
pipeline (see Algorithm~\ref{alg:incrementation}). It reads chunks from the BigBrain
image, increments the intensity value of each voxel by 1 for a specified amount of
iterations and write the result to an NFS as a Nifti image. Incrementing the data
reduce the caching effect. This experiment allows us to study the behavior of the
frameworks when all input are processed independently; i.e.\ each task in the graph
only depends on the previous one (see~\ref{Figure fig:tg-inc}).

This experiment refers to the implementation of the Spark pipelines purposed
in~\cite{Hayot-Sasson:17}.

>>>>

\subsubsection{PySpark RDD~\cite{spark-rdd}} Spark is a general-purpose big data
framework. It provides in-memory computing, data locality and lazy evaluation. Spark
abstract resilient distributed dataset (RDD)~\cite{RDD} making it fault-tolerant. Its
high-level API provides optimizations on the transformations made to some data. Since
Spark is written in Scala, this optimization is lessen because it requires a
serialization from Python to Java. The API offered by Spark is flexible and suit most
problem however it differ from Python ecosystem. The standalone scheduler is used for
our experiment. It has a LIFO policy.

\subsubsection{Dask Bag~\cite{dask-bag}} Dask Bag is one of the high-level API
offered by dask. It also provides in-memory computing, data locality and lazy
evaluation however it does not have fault resilience. Fundamently it is parallized
lists. Dask Bag parallelizes computations of large collection of generic python
objects~\cite{dask-bag}. Also, it offers optimized algorithm that mimic most the
toolz library. Our experiment use the dask distributed~\cite{dask-distributed}
scheduler. It has a LIFO policy. In theory it should speed-up the computation by
finishing task computations before starting new ones.

\subsubsection{Dask Delayed~\cite{dask-delayed}} Dask Delayed is a low-level API. It
does not offer the optimized algorithm as the high-level APIs however it allows the
user to parallelize custom function that do not fit in the array, dataframe or
MapReduce framework.

\subsubsection{Dask Futures~\cite{dask-futures}} Dask Futures is also a low-level API
from dask. It differs from the other APIs as its computations trigger immediately.

@@

%% Incrementation
\subsubsection{\textbf{Incrementation}}
As our first experiment to benchmark the frameworks we used a simple incrementation
pipeline (see Algorithm~\ref{alg:incrementation}). It reads chunks from the BigBrain
image, increments the intensity value of each voxel by 1 for a specified amount of
iterations and write the result to an NFS as a Nifti image. Incrementing the data
reduce the caching effect. This experiment allows us to study the behavior of the
frameworks when all input are processed independently; i.e.\ each task in the graph
only depends on the previous one (see Figure~\ref{Figure fig:tg-inc}). This mimic the
behavior of analyzing multiple independent subjects in parallel.

This experiment refers to the implementation of the Spark pipelines purposed
in Ref.~\cite{Hayot-Sasson:17}.
